Report - Latest Rodent Data

### 2019-03-05 index.Rmd
more website updates

Welcome to Portal Forecasting! This is a website run by the [Weecology](http://weecology.org/) group, interdisciplinary ecologists at the [University of Florida](http://www.wec.ufl.edu/). On this website, you'll find information about our ongoing efforts to forecast a time series of rodent abundances from [The Portal project](http://portal.weecology.org/), a long-term experimental monitoring project in desert ecology. Enjoy!

@@

>>>>

<br>

Welcome to Portal Forecasting! This is a website run by the [Weecology](http://weecology.org/) team, comprised of [Ethan White's](http://whitelab.weecology.org/) and [Morgan Ernest's](http://ernestlab.weecology.org/) lab groups at the [University of Florida](http://www.wec.ufl.edu/). We are a group of interdisciplinary ecologists broadly interested in collaborative approaches to empirical and computation ecology, open science, and open data.

On this website, you'll find information about our ongoing efforts to forecast a time series of rodent abundances from [The Portal project](http://portal.weecology.org/), a long-term experimental monitoring project in desert ecology. Enjoy!

<br>

@@

<br>

### 2019-03-05 report.Rmd
more website edits
more website updates

---
title: "Report - Latest Rodent Data"
---

Here's the most recent forecast for which observations have been made. The actual data (blue) are plotted in comparison to the forecast performed right before data collection (white, with error bars) for the control (unmanipulated) plots (top) and all plots together (bottom):
```{r, with_census_controls, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

>>>>

---
title: "Report - Latest Rodent Data"
---
<br>

Here's the most recent forecast for which observations have been made. The actual data (blue) are plotted in comparison to the forecast performed right before data collection (white, with error bars) for the control (unmanipulated) plots (top) and all plots together (bottom):

<br>

```{r, with_census_controls, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

<br>
